PM Mungbean meta-analysis

### 2021-09-12 02_Preliminary_analysis.Rmd
install bomrang package from github repo

```{r PA_Libraries, echo=TRUE, results='hide'}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               lubridate,
               openxlsx,
               devtools,
               reshape2,
               lme4,
               kableExtra,
               flextable,
               here,
               gridExtra)

>>>>

```{r PA_Libraries, echo=TRUE, results='hide'}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               lubridate,
               openxlsx,
               devtools,
               remotes,
               reshape2,
               lme4,
               kableExtra,
               flextable,
               here,
               gridExtra)
